SubsidyExplorer - Step 3: Classify vessels into management regimes

### 2022-04-29 scripts/03_management.Rmd
updating SI management plots in preparation for final submission

@@

```{r}
# Get eez codes and cooresponding territories/sovereigns
eez_info <- vessel_list_raw %>%
  group_by(eez_id) %>%
  distinct(eez_territory1_iso3, eez_territory2_iso3, eez_territory3_iso3, eez_sovereign1_iso3, eez_sovereign2_iso3, eez_sovereign3_iso3)

@@

  ggsave(paste0(results_dir, "fmi_score_map.png"), width = 7.5, height = 4, units = "in")
}
```

@@

  ggsave(paste0(results_dir, "fvfmsy_map.png"), width = 7.5, height = 9.5, units = "in")
}
```

# Proportion of formally assessed stocks by FAO region

# ```{r}
# prop_assessed_stocks <- costello_2016_upsides_dat %>%
#   group_by(region_fao_split) %>%
#   summarize(catch_ram = sum(catch[dbase == "RAM"]),
#             catch_other = sum(catch[dbase != "RAM"])) %>%
#   mutate(catch_prop_ram = catch_ram/(catch_ram + catch_other)) %>%
#   dplyr::select(fao_region = region_fao_split, catch_prop_ram)
# ```

# Proportion of catch share stocks by FAO region

# ```{r}
# prop_catch_share_stocks <- costello_2016_upsides_dat %>%
#   group_by(region_fao_split) %>%
#   summarize(catch_share= sum(catch[catch_share == 1]),
#             catch_other = sum(catch[catch_share != 1])) %>%
#   mutate(catch_prop_cs= catch_share/(catch_share + catch_other)) %>%
#   dplyr::select(fao_region = region_fao_split, catch_prop_cs)
# ```

@@

```{r}
vessel_list_manage <- vessel_list_raw %>%
  left_join(eez_management_indices, by = c("eez_id")) %>%
  left_join(median_fvfmsy_fao, by = c("fao_region"))
  # left_join(prop_assessed_stocks, by = c("fao_region")) %>%
  # left_join(prop_catch_share_stocks, by = c("fao_region"))

@@

write_csv(vessel_list_manage, paste0(results_dir, "vessel_list_2018_management.csv"))

# Calculate management quantiles for each indicator
fmi_quantile <- tibble("indicator" = "fmi") %>%
  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$fmi_best), nrow = 1)), names(quantile(vessel_list_manage$fmi_best))))

@@

```{r}

>>>>

}

# Save data files? 
save_files <- F
```

@@

```{r}
# Get eez codes and corresponding territories/sovereigns
eez_info <- vessel_list_raw %>%
  group_by(eez_id) %>%
  distinct(eez_territory1_iso3, eez_territory2_iso3, eez_territory3_iso3, eez_sovereign1_iso3, eez_sovereign2_iso3, eez_sovereign3_iso3)

@@

  ggsave(paste0(results_dir, "fmi_score_map.png"), width = 7.5, height = 4, units = "in")

  # Map by EEZ with the high seas FAO areas removed for PLOS ONE
  hs_color <- RColorBrewer::brewer.pal(9, "YlGn")[1]

  fmi_map_no_hs <- ggplot()+
    geom_sf(data = world, fill = "black", color = "grey", size = 0.25)+
    geom_sf(data = fmi_map_dat %>% dplyr::filter(!is.na(mrgid)), aes(fill = fmi_best), color = "grey", size = 0.25)+
    theme_bw()+
    scale_fill_distiller(palette = "YlGn", 
                         direction = 1,
                         limits = c(0.2, 1))+
    labs(fill = "FMI Score")+
    theme(plot.background = element_rect(color = NA),
          panel.border = element_rect(color = NA),
          panel.background = element_rect(fill = hs_color),
          axis.text = element_blank(),
          axis.ticks = element_blank())+
    coord_sf(expand = F)

  fmi_map_no_hs

  ggsave(paste0(results_dir, "fmi_scores_no_hs_map.png"), width = 7.5, height = 4, units = "in")
}
```

@@

  ggsave(paste0(results_dir, "fvfmsy_map.png"), width = 7.5, height = 9.5, units = "in")

  # Make PLOS ONE friendly version 
  fao_region_names <- c("77" = "Eastern Central part of the Pacific Ocean", 
                          "71" = "Western Central part of the Pacific Ocean",
                          "51" = "Western part of the Indian Ocean",
                          "61" = "Northwestern part of the Pacific Ocean",
                          "87" = "Southeastern part of the Pacific Ocean",
                          "41" = "Southwestern part of the Atlantic Ocean",
                          "34" = "Eastern Central part of the Atlantic Ocean",
                          "47" = "Southeastern part of the Atlantic Ocean",
                          "27" = "Northeastern part of the Atlantic Ocean",
                          "81" = "Southwestern part of the Pacific Ocean",
                          "21" = "Northwestern part of the Atlantic Ocean",
                          "57" = "Eastern part of the Indian Ocean",
                          "31" = "Western part of the Atlantic Ocean",
                          "67" = "Northeastern part of the Pacific Ocean",
                          "48" = "Antarctic part of the Atlantic Ocean",
                          "88" = "Antarctic part of the Pacific Ocean",
                          "58" = "Antarctic and Southern parts of the Indian Ocean",
                          "18" = "Arctic Ocean",
                          "37" = "Mediterranean and Black Sea")

    fao_region_names_df <- tibble(fao_region = as.integer(names(fao_region_names)),
                                  name = fao_region_names)

  fvfmsy_plot_dat <- fvfmsy_map_dat %>%
    st_drop_geometry() %>%
    left_join(fao_region_names_df, by = "fao_region") %>%
    mutate(display_name = paste0("Area ", fao_region, ": ", name))

  fvfmsy_plot <- ggplot()+
    geom_hline(yintercept = 1)+
    geom_point(data = fvfmsy_plot_dat, aes(x = as.factor(display_name), y = value, fill = value, shape = metric_display), size = 3)+
    theme_bw()+
    scale_x_discrete(limits=rev)+
    coord_flip()+
    scale_fill_gradient2(low = "blue",
                         high = 'red',
                         mid = "white",
                         midpoint = 1,
                         limits = c(0,5),
                         oob = scales::squish)+
    labs(fill = "F/Fmsy", shape = "Value", x = "", y = "F/Fmsy")+
    guides(fill = "none")+
    scale_shape_manual(values = c(21,22,23))+
    theme(plot.background = element_rect(color = NA),
          #panel.border = element_rect(color = NA),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = "bottom")

    ggsave(paste0(results_dir, "fvfmsy_plot.png"), width = 7.5, height = 5, units = "in")

<!-- # Proportion of formally assessed stocks by FAO region -->

<!-- # ```{r} -->
<!-- # prop_assessed_stocks <- costello_2016_upsides_dat %>% -->
<!-- #   group_by(region_fao_split) %>% -->
<!-- #   summarize(catch_ram = sum(catch[dbase == "RAM"]), -->
<!-- #             catch_other = sum(catch[dbase != "RAM"])) %>% -->
<!-- #   mutate(catch_prop_ram = catch_ram/(catch_ram + catch_other)) %>% -->
<!-- #   dplyr::select(fao_region = region_fao_split, catch_prop_ram) -->
<!-- # ``` -->

<!-- # Proportion of catch share stocks by FAO region -->

<!-- # ```{r} -->
<!-- # prop_catch_share_stocks <- costello_2016_upsides_dat %>% -->
<!-- #   group_by(region_fao_split) %>% -->
<!-- #   summarize(catch_share= sum(catch[catch_share == 1]), -->
<!-- #             catch_other = sum(catch[catch_share != 1])) %>% -->
<!-- #   mutate(catch_prop_cs= catch_share/(catch_share + catch_other)) %>% -->
<!-- #   dplyr::select(fao_region = region_fao_split, catch_prop_cs) -->
<!-- # ``` -->

@@

```{r}
# Apply management scores to vessel list
vessel_list_manage <- vessel_list_raw %>%
  left_join(eez_management_indices, by = c("eez_id")) %>%
  left_join(median_fvfmsy_fao, by = c("fao_region"))

@@

if(save_files){
write_csv(vessel_list_manage, paste0(results_dir, "vessel_list_2018_management.csv"))
}
```

```{r}
# Calculate management quantiles for each indicator
fmi_quantile <- tibble("indicator" = "fmi") %>%
  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$fmi_best), nrow = 1)), names(quantile(vessel_list_manage$fmi_best))))

@@
